\documentclass[12pt,letter]{article}
\title{VSCode + LaTeX Workshop}
\author{aniyadav90}
\begin{document}
\maketitle
\section{Section}
OK here we go. Here is some content

\section{Basic usage}
\begin{itemize}
    \item Open PDF viewer: \texttt{cmd + option + V} (the viewer doesn't open by default, so you need to do this after opening a .tex file). You only need to do this once. The PDF gets refreshed on each build.
    \item Build: \texttt{cmd + option + B} / \texttt{cmd + S} (auto-build on save)
\end{itemize}
With the following options LaTeX-Workshop feels similar to TeXShop:
\begin{verbatim}
    "latex-workshop.view.pdf.viewer": "tab",
    "latex-workshop.synctex.afterBuild.enabled": true
\end{verbatim}

\section{Pros and cons}
\subsection{Pros}
\begin{itemize}
    \item VSCode is a much (!) better text editor compared to TeXShop.
    \item Dedicated keyboard shortcuts for common environments
\end{itemize}
\subsection{Cons}
\begin{itemize}
    \item Using an external PDF viewer doesn't work well. This means that you can't have your text editor and PDF on separate desktops, which was a nice feature of using TeXShop.\footnote{To be a bit more concrete about this, you \textit{can} use an external viewer, it's just not ``officially supported'', and the experience isn't as good as TeXShop's external viewer. For example, (when using Preview as the external viewer) on each build, the zoom-level resets to its default, rather than retaining the desired zoom level. Also, from looking around the web, it seems like it's tricky to get synctex working with an external viewer, which sucks because automatically synctex-ing after build is very nice (and replicates the TeXShop experience.)} 
\end{itemize}




\end{document}